Considering scale in multilayer animal social networks

### 2020-06-13 paper/manuscript.Rmd
todo

The ordinal multilayer network generated from discrete time windows indicated 
within-year periods of increased caribou sociality. Edge overlap

(Figure \@ref(fig:temp) )
These
results suggest that an increasing window length, especially for the summer
season, may be resulting in less precisely defined seasons that are not clearly
capturing periods of aggregation and dissaggregation related to resource
availability.

@@

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics appeared to stabilize. Mean graph
strength was consistently weak in summer layers but varied in winter layers at
low number of observations, becoming stable at ~75 observations (Figure
\@ref(fig:nobs)a). Layer relevance in the summer was consistently low, but
winter layers increased between approximately 10  and 100  observations,
remaining stable with additional observations (Figure \@ref(fig:nobs)b). Like
coarse land cover resolution (Figure \@ref(fig:lcres)), low numbers of
observations were not sufficient for capturing individuals in all contexts and
therefore layer similarity could not be calculated below ~30 observations for
forest, approximately ~80 observations for open (Figure \@ref(fig:nobs)c). Layer
similarity was not possible to calculate for forage layers because there were no
connected individuals in summer forage. Once sufficient observations were
obtained, layer similarity showed some variability with increasing numbers of
observations for forest and was relatively stable in open layers. Connective
redundancy increased dramatically between ~10 and ~50 observations before
stabilizing with additional observations included (Figure \@ref(fig:nobs)d).
Given the observed trend of these multilayer metrics stabilizing after a certain
number of observations are included, the results suggest this sensitivity method
could be useful for determining the number of observations necessary for
sufficiently describing social dynamics across contexts.

>>>>

<!-- TODO add? each ordinal network layer consisted of avg 380 fixes * ID -->

The ordinal multilayer network generated from discrete time windows indicate
within-year periods of increased caribou sociality. Edge overlap was higher in time windows 1, 6-11 and 15-20 than time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). These periods between approximately October and May

increasing graph strength with overall peak in 2018 but still increases in 2019
note graph connectedness is evident panel B

<!-- Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20). B) Ordinal network layers showing unweighted edges between individuals within time windows. Like edge overlap, individuals were more connected in time window 1, 6-11, and 15-20, compared to 2-5 and 12-15. C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines. Graph strength peaked in time window 9, with noticeable higher strength than the following year.  -->
These
results suggest that an increasing window length, especially for the summer
season, may be resulting in less precisely defined seasons that are not clearly
capturing periods of aggregation and dissaggregation related to resource
availability.

@@

<!-- TODO: reduce to this version -->
As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics appeared to stabilize. Mean graph
strength was consistently weak in summer layers but varied in winter layers at
low number of observations, becoming stable at ~75 observations (Figure
\@ref(fig:nobs)a). Layer relevance in the summer was consistently low, but
winter layers increased between approximately 10  and 100  observations,
remaining stable with additional observations (Figure \@ref(fig:nobs)b). Like
coarse land cover resolution (Figure \@ref(fig:lcres)), low numbers of
observations were not sufficient for capturing individuals in all contexts and
therefore layer similarity could not be calculated below ~30 observations for
forest, approximately ~80 observations for open (Figure \@ref(fig:nobs)c). Layer
similarity was not possible to calculate for forage layers because there were no
connected individuals in summer forage. Once sufficient observations were
obtained, layer similarity showed some variability with increasing numbers of
observations for forest and was relatively stable in open layers. Connective
redundancy increased dramatically between ~10 and ~50 observations before
stabilizing with additional observations included (Figure \@ref(fig:nobs)d).
Given the observed trend of these multilayer metrics stabilizing after a certain
number of observations are included, the results suggest this sensitivity method
could be useful for determining the number of observations necessary for
sufficiently describing social dynamics across contexts.
